Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
Add short sketch for algorithm to close properties

\begin{quote}
    \emph{TBD: describe the algorithm}
\end{quote}

@@

>>>>

@@

\begin{quote}
    TBD: describe the algorithm

    Below is the schematic algorithm, from my original mail to kazu:
\end{quote}

\noindent \verb|xs| is a free variable here.  So we would need to
close that term by transforming it to:

\begin{quote}\small\begin{verbatim}
\xs -> sort xs == sort (sort (xs::[Int]))
\end{verbatim}\end{quote}

\noindent I imagine this could work by performing those steps:

\begin{enumerate}

    \item
        parse the property with e.g. haskell-src (never used it, so
        I'm not sure if it allows you to parse code snippets)

    \item
        Load the module containing the DocProperty with hint, and try
        to look up all variables used by the property (\verb|sort| and
        \verb|xs| for the example above).

    \item
        Close the term over all variables, for which lookup failed,
        load it with hint and test it with quickCheck.
\end{enumerate}
